\input{title.tex}

### 2023-07-31 docs/papers/04_response_letter/source/reviewer_1.tex
fix(project): :memo: update response linenos

\RC{} In Eq 1, $X_0$ and $X_1$ were never defined.

\RC{} Using ``$*$'' to denote the dimension of a matrix (e.g., $k*k$) is a bit odd; please consider using a multiplication symbol, e.g., $k \times k$.

\AR{} We have revised the description of the DSC method to make it clearer and more comprehensive. We expanded on the purpose and process of the DSC method, provided more context on how it fits into our research, and clarified the mathematical notation. We also explained the specific variables used when we introduced $X_1, X_0, Z_1$, and $Z_0$, as well as mentioned the specific method used for minimization and the corresponding reference. We believe that these revisions have significantly improved the clarity of our method description.

@@

\begin{quote}[page=5, sline=89, eline=91]
    In the methodology section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as organizational diagrams during different periods of time.
\end{quote}

\begin{quote}[page=5, sline=98, eline=99]
    An organizational diagram is widely used to depict SES structures by abstracting links and nodes from the real-world interactions~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
\end{quote}

@@

\begin{quote}[page=5, sline=99, eline=103]
    We apply the analysis of the organizational diagrams~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
    We examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray the organizational diagrams in this study~\cite{bodin2017a,kluger2020,guerrero2015}.
\end{quote}

@@

\begin{quote}[page=7, sline=162, eline=163]
    Two primary methods can be employed to validate the efficiency of the DSC approach.
\end{quote}

\begin{quote}[page=8, sline=169, eline=172]
    An effective result would be one where a significant difference is observed after treatment but not before treatment. If this is not the case, it implies that the institutional changes were ineffective for the treated units.
\end{quote}

\begin{quote}[page=8, sline=180, eline=184]
    If the ratio of the root mean square error (see Equation~3) in the pre-synthesis period is significantly higher for most provinces (again using the $T$ test to determine the significance of the difference) than the results of other placebo units, the provinces in the YRB was more significantly affected than most other provinces during the treatment periods ($1987$ and $1998$), i.e., more effective.
\end{quote}

@@

\begin{quote}[page=8, sline=173, eline=174]
    Secondly, placebo tests are another common way to evaluate the effectiveness of synthetic control methods~\cite{abadie2010}.
\end{quote}

@@

\begin{quote}[page=4, sline=74, eline=75]
    In $1980s$, the central government proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019d, wang2019e}.
\end{quote}

@@

\begin{quote}[page=8, sline=169, eline=172]
    An effective result would be one where a significant difference is observed after treatment but not before treatment. If this is not the case, it implies that the institutional changes were ineffective for the treated units.
\end{quote}

@@

\begin{quote}[page=10, sline=208, eline=210]
    From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
\end{quote}

@@

\begin{quote}[page=14, sline=267, eline=270]
    Secondly, a theoretical marginal benefit analysis (see \textit{Appendix C}) suggests that this ``major users are effected more'' pattern can be inferred from a simple assumption that stakeholders anticipate future value in water quotas, thereby lending further support to the above hypothesis.
.
\end{quote}

>>>>

\RC*{} In Eq 1, $X_0$ and $X_1$ were never defined.

\RC*{} Using ``$*$'' to denote the dimension of a matrix (e.g., $k*k$) is a bit odd; please consider using a multiplication symbol, e.g., $k \times k$.

\AR{} [page 6 to 8, lines 124 to 185] We have revised the description of the DSC method to make it clearer and more comprehensive. We expanded on the purpose and process of the DSC method, provided more context on how it fits into our research, and clarified the mathematical notation. We also explained the specific variables used when we introduced $X_1, X_0, Z_1$, and $Z_0$, as well as mentioned the specific method used for minimization and the corresponding reference. We believe that these revisions have significantly improved the clarity of our method description.

@@

\begin{quote}[page=5, sline=90, eline=92]
    In this section, we first utilize the descriptions of official documents following the two institutional shifts to abstract the interactions of SES into structures as organizational diagrams during different periods of time.
\end{quote}

\begin{quote}[page=5, sline=99, eline=100]
    An organizational diagram is widely used to depict SES structures by abstracting links and nodes from the real-world interactions~\cite{wang2022g,bodin2017a,kluger2020,guerrero2015}.
\end{quote}

@@

\begin{quote}[page=5, sline=100, eline=105]
    We apply the analysis of the organizational diagrams~\cite{bodin2017b} to portray SES structures by abstracting relationships between ecological units (river reaches), stakeholders (provinces), and the administrative unit at the basin scale (the Yellow River Conservancy Commission) into structural patterns from official documents.
    We examined the official documents of the two institutional shifts (87-WAS and 98-UBR) to portray the organizational diagrams in this study~\cite{bodin2017a,kluger2020,guerrero2015}.
\end{quote}

@@

\begin{quote}[page=7, sline=163]
    The efficiency of the DSC approach can be validated using two primary methods.
\end{quote}

\begin{quote}[page=8, sline=170, eline=172]
    A significant difference observed after treatment, but not before, indicates that the policy was effective.
    If this pattern is not found, it suggests that the institutional changes did not impact the treated units.
\end{quote}

\begin{quote}[page=8, sline=180, eline=184]
    If the ratio of the Root Mean Square Error (RMSE) (see Equation 3) in the post/pre -treated period is significantly higher for most treated provinces (using the T test to assess significance) compared to other placebo units, it implies that the provinces in the YRB were significantly affected during the treatment periods (1987 and 1998), thus indicating effectiveness.
\end{quote}

@@

\begin{quote}[page=8, sline=173, eline=174]
    The second method involves using placebo tests, a standard procedure for assessing the effectiveness of synthetic control methods~\cite{abadie2010}.
\end{quote}

@@

\begin{quote}[page=4, sline=75, eline=76]
    In $1980s$, the central government proposed to develop a water resource allocation institution for the Yellow River~\cite{wang2019d, wang2019e}.
\end{quote}

@@

\begin{quote}[page=8, sline=170, eline=172]
    A significant difference observed after treatment, but not before, indicates that the policy was effective.
    If this pattern is not found, it suggests that the institutional changes did not impact the treated units.
\end{quote}

@@

\begin{quote}[page=10, sline=207, eline=209]
    From 1988 to 1998, on average, while the estimation of annual water use only suggests $887.05$ billion $m^3$, the observed water use of the YRB provinces reached $938.06$ billion $m^3$ (an increase of $5.75\%$).
\end{quote}

@@

\begin{quote}[page=14, sline=266, eline=269]
    Secondly, a theoretical marginal benefit analysis (see \textit{Appendix C}) suggests that this ``major users are effected more'' pattern can be inferred from a simple assumption that stakeholders anticipate future value in water quotas, thereby lending further support to the above hypothesis.
\end{quote}

### 2023-07-31 docs/papers/04_response_letter/source/reviewer_2.tex
fix(project): :memo: update response linenos

\begin{quote}[page=6, sline=124, eline=133]
    The Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021} is a tool we use to estimate how water use might have evolved if there had been no institutional shift.
    Think of it as creating an alternate reality or a ``what-if'' scenario to compare with what actually happened~\cite{abadie2010, abadie2015, hill2021}.
    The key idea behind this method is to evaluate the effects of policy changes that mainly affect certain units (in this case, the institutional shifts in the Yellow River Basin or YRB).
    The method creates a ``synthetic'' version of the affected units by combining information from other similar but unaffected units. This ``synthetic'' version serves as a control group, which we can compare with the actual affected units.
    The DSC method, therefore, is a powerful tool as it allows us to control for unobserved factors that can change over time, providing more robust results.
\end{quote}

@@

\AR{} We appreciate your thoughtful suggestion about additional checks for our Differenced Synthetic Control (DSC) method. We now revised the term from ``robustness'' to ``efficiency'' based on the comments from the reviewer \#1, so we basically kept the tests section without additional approach for the following reasons:

>>>>

\begin{quote}[page=6, sline=124, eline=132]
    The Differenced Synthetic Control (DSC) method~\cite{arkhangelsky2021} is a tool we use to estimate how water use might have evolved if there had been no institutional shift.
    Think of it as creating an alternate reality or a ``what-if'' scenario to compare with what actually happened~\cite{abadie2010, abadie2015, hill2021}.
    The key idea behind this method is to evaluate the effects of policy changes (in this case, the 87-WAS and the 98-UBR) that mainly affect certain units (the provinces in the YRB).
    The method creates a ``synthetic'' version of the affected units by combining information from other similar but unaffected units. This ``synthetic'' version serves as a control group, which we can compare with the actual affected units.
    The DSC method, therefore, is a powerful tool as it allows us to control for unobserved factors that can change over time.
\end{quote}

@@

\AR{} We appreciate your thoughtful suggestion about additional checks for our Differenced Synthetic Control (DSC) method. We now revised the term from ``robustness'' to ``efficiency'' based on the comments from the reviewer \#1, so we basically kept the previous testing approaches for the following reasons:
